The \dealii{} Library, Version 8.5

### 2017-03-03 8.5/paper.tex
Added TODO for Luca.

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Denis Davydov,
    Timo Heister,
    Matthias Maier,
    Jean-Paul Pelteret
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[4]{Matthias Maier}
\affil[4]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}

\author[5]{Jean-Paul Pelteret}
\affil[5]{Chair of Applied Mechanics, 
  University of Erlangen-Nuremberg, 
  Egerlandstr.\ 5, 
  91058 Erlangen, 
  Germany.
  {\texttt{jean-paul.pelteret@fau.de}}}

@@

\item The \texttt{MappingManifold} class provides mappings between the
  reference cell and a mesh cell that is ``exact'' in the sense that
  the edges, faces, and the interior of the mesh cell matches an
  underlying manifold. This is opposed to using the usual polynomial
  approximations of the manifold.

@@

>>>>

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Matthias Maier,
    Jean-Paul Pelteret
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[4]{Luca Heltai}
\affil[4]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265, 
  34136, Trieste, Italy
{\texttt{luca.heltai@sissa.it}}}

\author[5]{Matthias Maier}
\affil[5]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}

\author[6]{Jean-Paul Pelteret}
\affil[6]{Chair of Applied Mechanics, 
  University of Erlangen-Nuremberg, 
  Egerlandstr.\ 5, 
  91058 Erlangen, 
  Germany.
  {\texttt{jean-paul.pelteret@fau.de}}}

@@

\item The \texttt{MappingManifold} class provides mappings between the
  reference cell and a mesh cell that is ``exact'' in the sense that
  the edges, faces, and the interior of the mesh cell matches an
  underlying manifold. This is opposed to using the usual polynomial
  approximations of the manifold.
  TODO: Luca

@@

TODO: Luca
